Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-04-02 paper.tex
update

Step 3 and Step 4: These two steps follow the standard PSO steps \cite{shi2001particle} except for some differences in particles mapping and decoding processes. In particular, these two differences are related to sorting a created service queue using serivce-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a $WG$ respectively. Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in \ref{POS-based_algomargin}.

@@

In this work, we propose an effective PSO-based approach to comprehensive quality-aware semantic web service composition, which also has shown promise in achieving a better comprehensive quality in terms of a combination of semantic matchmaking quality and QoS compared to exisitng works. Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.

>>>>

Step 3 and Step 4: These two steps follow the standard PSO steps \cite{shi2001particle} except for some differences in particles mapping and decoding processes. In particular, these two differences are related to sorting a created service queue using service-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a $WG$ respectively. Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in \ref{POS-based_algomargin}.

@@

In this work, we propose an effective PSO-based approach to comprehensive quality-aware semantic web service composition, which also has shown promise in achieving a better comprehensive quality in terms of a combination of semantic matchmaking quality and QoS compared to existing works. Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.
